---
title: "capstone_Import_Tidy_Export"
author: "Fiona Neilson"
date: "26/09/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyr) 
library(dplyr) 
library(tibble)
```

## READ IN THE DATA

Dan <- read.csv("t3_final_Dan_.csv", stringsAsFactors = TRUE, header = FALSE)

# Batch 1

```{r}
#Batch 1 (20 files)
DanSerbian <- read.csv("t3_final_Dan_Serbian.csv", stringsAsFactors = TRUE, header = FALSE)
DanSinhalese <- read.csv("t3_final_Dan_Sinhalese.csv", stringsAsFactors = TRUE, header = FALSE)
DanSpanish <- read.csv("t3_final_Dan_Spanish.csv", stringsAsFactors = TRUE, header = FALSE)
DanTamil <- read.csv("t3_final_Dan_Tamil.csv", stringsAsFactors = TRUE, header = FALSE)
DanTurkish <- read.csv("t3_final_Dan_Turkish.csv", stringsAsFactors = TRUE, header = FALSE)
DanUrdu <- read.csv("t3_final_Dan_Urdu.csv", stringsAsFactors = TRUE, header = FALSE)
DanAlbanian <- read.csv("t3_final_Dan_Albanian.csv", stringsAsFactors = TRUE, header = FALSE)
DanBurmese <- read.csv("t3_final_Dan_Burmese.csv", stringsAsFactors = TRUE, header = FALSE)
DanHindi <- read.csv("t3_final_Dan_Hindi.csv", stringsAsFactors = TRUE, header = FALSE)
DanItalian <- read.csv("t3_final_Dan_Italian.csv", stringsAsFactors = TRUE, header = FALSE)
DanArabic <- read.csv("t3_final_Dan_Arabic.csv", stringsAsFactors = TRUE, header = FALSE)
DanCantonese <- read.csv("t3_final_Dan_Cantonese.csv", stringsAsFactors = TRUE, header = FALSE)
DanDari<- read.csv("t3_final_Dan_Dari.csv", stringsAsFactors = TRUE, header = FALSE)
DanGreek<- read.csv("t3_final_Dan_Greek.csv", stringsAsFactors = TRUE, header = FALSE)
DanHazaraghi<- read.csv("t3_final_Dan_Hazaraghi.csv", stringsAsFactors = TRUE, header = FALSE)
DanKhmer<- read.csv("t3_final_Dan_Khmer.csv", stringsAsFactors = TRUE, header = FALSE)
DanMandarin<- read.csv("t3_final_Dan_Mandarin.csv", stringsAsFactors = TRUE, header = FALSE)
DanPunjabi<- read.csv("t3_final_Dan_Punjabi.csv", stringsAsFactors = TRUE, header = FALSE)
DanTigrinya <- read.csv("t3_final_Dan_Tigrinya.csv", stringsAsFactors = TRUE, header = FALSE)
DanVietnamese<- read.csv("t3_final_Dan_Vietnamese.csv", stringsAsFactors = TRUE, header = FALSE)
```

## CREATE FUNCTIONS

```{r}
# define counting obs function 
count_obs <- function(x) {
  x2 <- data.frame(t(x[-1]))
  colnames(x2) <- x[, 1]
  x2 <- remove_rownames(x2)
  x3 <- x2 %>% gather(Male, Female, key = "SEXP", value = "Count")
  x3 %>% 
  summarise(
    valid = sum(Count != 0),
    missing = sum(Count == 0)
  )
  }
```


```{r}
#define tidy function
tidy <- function(x) {
  x2 <- data.frame(t(x[-1]))
  colnames(x2) <- x[, 1]
  x2 <- remove_rownames(x2)
  x3 <- x2 %>% gather(Male, Female, key = "SEXP", value = "Count")
}
```


```{r}
DanSerbian
```

```{r}
Serb2 <- tidy(DanSerbian)
Serb2
```

```{r}
colnames(Serb2)
```


## APPLY FUNCTIONS

**tidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
# save output with Dan prefix removed
Serbian <- tidy(DanSerbian)
Sinhalese <- tidy(DanSinhalese)
Spanish <- tidy(DanSpanish)
Tamil <- tidy(DanTamil)
Turkish <- tidy(DanTurkish)
Urdu <- tidy(DanUrdu)
Albanian <- tidy(DanAlbanian)
Burmese <- tidy(DanBurmese)
Hindi <- tidy(DanHindi)
Italian <- tidy(DanItalian)
Arabic <- tidy(DanArabic)
Cantonese <- tidy(DanCantonese)
Dari<- tidy(DanDari)
Greek <- tidy(DanGreek)
Hazaraghi <- tidy(DanHazaraghi)
Khmer <- tidy(DanKhmer)
Mandarin <- tidy(DanMandarin)
Punjabi <- tidy(DanPunjabi)
Tigrinya <- tidy(DanTigrinya)
Vietnamese <- tidy(DanVietnamese)
```


```{r}
colnames(Hakka)
```
```{r}
colnames(Greek)
```
```{r}
names <- c("LGA", "LANP", "HEAP", "EETP",  "NEDD",  "ENGP", "BPLP", "YARRP", "SEXP","Count")
names
```
```{r}
names(Greek) <- names
head(Greek)
```
```{r}
names(Vietnamese) <- names
head(Vietnamese)
```


**count obs**
count_obs(x) * use original file with Dan prefix

```{r}
count_obs(DanSerbian)
count_obs(DanSinhalese)
count_obs(DanSpanish)
count_obs(DanTamil)
count_obs(DanTurkish)
count_obs(DanUrdu)
count_obs(DanAlbanian)
count_obs(DanBurmese)
count_obs(DanHindi)
count_obs(DanItalian)
count_obs(DanArabic)
count_obs(DanCantonese)
count_obs(DanDari)
count_obs(DanGreek)
count_obs(DanHazaraghi)
count_obs(DanKhmer)
count_obs(DanMandarin)
count_obs(DanPunjabi)
count_obs(DanTigrinya)
count_obs(DanVietnamese)

```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(Serbian,"Serbian.csv", row.names = FALSE)
write.csv(Sinhalese,"Sinhalese.csv", row.names = FALSE) 
write.csv(Spanish, "Spanish.csv", row.names = FALSE)
write.csv(Tamil, "Tamil.csv", row.names = FALSE)
write.csv(Turkish, "Turkish.csv", row.names = FALSE)
write.csv(Urdu, "Urdu.csv", row.names = FALSE)
write.csv(Albanian, "Albanian.csv", row.names = FALSE)
write.csv(Burmese, "Burmese.csv", row.names = FALSE)
write.csv(Hindi, "Hindi.csv", row.names = FALSE)
write.csv(Italian, "Italian.csv", row.names = FALSE) 
write.csv(Arabic, "Arabic.csv", row.names = FALSE) 
write.csv(Cantonese, "Cantonese.csv", row.names = FALSE)
write.csv(Dari, "Dari.csv", row.names = FALSE)
write.csv(Greek, "Greek.csv", row.names = FALSE) 
write.csv(Hazaraghi, "Hazaraghi.csv", row.names = FALSE) 
write.csv(Khmer, "Khmer.csv", row.names = FALSE) 
write.csv(Mandarin, "Mandarin.csv", row.names = FALSE) 
write.csv(Punjabi, "Punjabi.csv", row.names = FALSE) 
write.csv(Tigrinya, "Tigrinya.csv", row.names = FALSE) 
write.csv(Vietnamese, "Vietnamese.csv", row.names = FALSE)
```

# Batch 2

```{r}
DanBosnian <- read.csv("t3_final_Dan_Bosnian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMalayalam <- read.csv("t3_final_Dan_Malayalam.csv", stringsAsFactors = TRUE, header = FALSE)
DanTagalog <- read.csv("t3_final_Dan_Tagalog.csv", stringsAsFactors = TRUE, header = FALSE)
DanFrench <- read.csv("t3_final_Dan_French.csv", stringsAsFactors = TRUE, header = FALSE)
DanPersian_ex_Dari <- read.csv("t3_final_Dan_Persian_ex_Dari.csv", stringsAsFactors = TRUE, header = FALSE)
DanCroatian <- read.csv("t3_final_Dan_Croatian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMin_Nan <- read.csv("t3_final_Dan_Min_Nan.csv", stringsAsFactors = TRUE, header = FALSE)
DanPashto <- read.csv("t3_final_Dan_Pashto.csv", stringsAsFactors = TRUE, header = FALSE)
DanPolish <- read.csv("t3_final_Dan_Polish.csv", stringsAsFactors = TRUE, header = FALSE)
DanSamoan <- read.csv("t3_final_Dan_Samoan.csv", stringsAsFactors = TRUE, header = FALSE)
DanFilipino <- read.csv("t3_final_Dan_Filipino.csv", stringsAsFactors = TRUE, header = FALSE)
DanBengali <- read.csv("t3_final_Dan_Bengali.csv", stringsAsFactors = TRUE, header = FALSE)
DanTelugu <- read.csv("t3_final_Dan_Telugu.csv", stringsAsFactors = TRUE, header = FALSE)
DanGujarati <- read.csv("t3_final_Dan_Gujarati.csv", stringsAsFactors = TRUE, header = FALSE)
DanIndonesian <- read.csv("t3_final_Dan_Indonesian.csv", stringsAsFactors = TRUE, header = FALSE)
DanRohingya <- read.csv("t3_final_Dan_Rohingya.csv", stringsAsFactors = TRUE, header = FALSE)
DanThai <- read.csv("t3_final_Dan_Thai.csv", stringsAsFactors = TRUE, header = FALSE)
DanRussian <- read.csv("t3_final_Dan_Russian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHungarian <- read.csv("t3_final_Dan_Hungarian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHakka <- read.csv("t3_final_Dan_Hakka.csv", stringsAsFactors = TRUE, header = FALSE)
```

## APPLY FUNCTIONS

**yidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
# save output with Dan prefix removed
Bosnian <- tidy(DanBosnian)
Malayalam <- tidy(DanMalayalam)
Tagalog <- tidy(DanTagalog)
French <- tidy(DanFrench)
Persian_ex_Dari <- tidy(DanPersian_ex_Dari)
Croatian <- tidy(DanCroatian)
Min_Nan <- tidy(DanMin_Nan)
Pashto <- tidy(DanPashto)
Polish <- tidy(DanPolish)
Samoan <- tidy(DanSamoan)
Filipino <- tidy(DanFilipino)
Bengali <- tidy(DanBengali)
Telugu <- tidy(DanTelugu)
Gujarati <- tidy(DanGujarati)
Indonesian <- tidy(DanIndonesian)
Rohingya <- tidy(DanRohingya)
Thai <- tidy(DanThai)
Russian <- tidy(DanRussian)
Hungarian <- tidy(DanHungarian)
Hakka <- tidy(DanHakka)
```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(Bosnian, "Bosnian.csv", row.names = F)
write.csv(Malayalam, "Malayalam.csv", row.names = F)
write.csv(Tagalog,"Tagalog.csv", row.names = F )
write.csv(French, "French.csv", row.names = F)
write.csv(Persian_ex_Dari, "Persian_ex_Dari.csv", row.names = F)
write.csv(Croatian, "Croatian.csv", row.names = F)
write.csv(Min_Nan, "Min_Nan.csv", row.names = F)
write.csv(Pashto, "Pashto.csv", row.names = F)
write.csv(Polish, "Polish.csv", row.names = F)
write.csv(Samoan, "Samoan.csv", row.names = F)
write.csv(Filipino, "Filipino.csv", row.names = F)
write.csv(Bengali, "Bengali.csv", row.names = F)
write.csv(Telugu,"Telugu.csv", row.names = F )
write.csv(Gujarati, "Gujarati.csv", row.names = F)
write.csv(Indonesian, "Indonesian.csv", row.names = F)
write.csv(Rohingya, "Rohingya.csv", row.names = F)
write.csv(Thai, "Thai.csv", row.names = F)
write.csv(Russian, "Russian.csv", row.names = F)
write.csv(Hungarian, "Hungarian.csv", row.names = F)
write.csv(Hakka, "Hakka.csv", row.names = F)
```

## READ IN THE DATA

Dan <- read.csv("t3_final_Dan_.csv", stringsAsFactors = TRUE, header = FALSE)

# Batch 3

```{r}
DanKorean <- read.csv("t3_final_Dan_Korean.csv", stringsAsFactors = TRUE, header = FALSE)
DanRomanian <- read.csv("t3_final_Dan_Romanian.csv", stringsAsFactors = TRUE, header = FALSE)
DanKannada <- read.csv("t3_final_Dan_Kannada.csv", stringsAsFactors = TRUE, header = FALSE)
DanMacedonian <- read.csv("t3_final_Dan_Macedonian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMalay <- read.csv("t3_final_Dan_Malay.csv", stringsAsFactors = TRUE, header = FALSE)
DanSomali <- read.csv("t3_final_Dan_Somali.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaoriCookIsland <- read.csv("t3_final_Dan_Maori_Cook_Island.csv", stringsAsFactors = TRUE, header = FALSE)
DanGerman <- read.csv("t3_final_Dan_German.csv", stringsAsFactors = TRUE, header = FALSE)
DanChineseNfd <- read.csv("t3_final_Dan_Chinese_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanMauritianCreole <- read.csv("t3_final_Dan_Mauritian_Creole.csv", stringsAsFactors = TRUE, header = FALSE)
DanOromo <- read.csv("t3_final_Dan_Oromo.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaltese <- read.csv("t3_final_Dan_Maltese.csv", stringsAsFactors = TRUE, header = FALSE)
DanNuer <- read.csv("t3_final_Dan_Nuer.csv", stringsAsFactors = TRUE, header = FALSE)
DanNepali <- read.csv("t3_final_Dan_Nepali.csv", stringsAsFactors = TRUE, header = FALSE)
DanArmenian <- read.csv("t3_final_Dan_Armenian.csv", stringsAsFactors = TRUE, header = FALSE)
DanSouthernAsianNfd <- read.csv("t3_final_Dan_Southern_Asian_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanLao <- read.csv("t3_final_Dan_Lao.csv", stringsAsFactors = TRUE, header = FALSE)
DanPortugese <- read.csv("t3_final_Dan_Portugese.csv", stringsAsFactors = TRUE, header = FALSE)
DanMarathi <- read.csv("t3_final_Dan_Marathi.csv", stringsAsFactors = TRUE, header = FALSE)
DanJapanese <- read.csv("t3_final_Dan_Japanese.csv", stringsAsFactors = TRUE, header = FALSE)
```

## APPLY FUNCTIONS

**tidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
# save output with Dan prefix removed
Korean <- tidy(DanKorean) 
Romanian <- tidy(DanRomanian)
Kannada  <- tidy(DanKannada) 
Macedonian <- tidy(DanMacedonian) 
Malay <- tidy(DanMalay)
Somali <- tidy(DanSomali)
MaoriCookIsland  <- tidy(DanMaoriCookIsland) 
German <- tidy(DanGerman) 
ChineseNfd  <- tidy(DanChineseNfd)
MauritianCreole  <- tidy(DanMauritianCreole) 
Oromo <- tidy(DanOromo)
Maltese  <- tidy(DanMaltese) 
Nuer  <- tidy(DanNuer)
Nepali  <- tidy(DanNepali)
Armenian <- tidy(DanArmenian)
SouthernAsianNfd <- tidy(DanSouthernAsianNfd) 
Lao <- tidy(DanLao) 
Portugese <- tidy(DanPortugese)
Marathi <- tidy(DanMarathi) 
Japanese <- tidy(DanJapanese) 
```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(Korean, "Korean.csv", row.names = F)
write.csv(Romanian, "Romanian.csv", row.names = F)
write.csv(Kannada, "Kannada.csv", row.names = F)
write.csv(Macedonian,"Macedonian.csv", row.names = FALSE)
write.csv(Malay,"Malay.csv", row.names = FALSE)
write.csv(Somali,"Somali.csv", row.names = FALSE)
write.csv(MaoriCookIsland,"MaoriCookIsland.csv", row.names = FALSE)
write.csv(German,"German.csv", row.names = FALSE)
write.csv(ChineseNfd,"ChineseNfd.csv", row.names = FALSE)
write.csv(MauritianCreole,"MauritianCreole.csv", row.names = FALSE)
write.csv(Oromo,"Oromo.csv", row.names = FALSE)
write.csv(Maltese,"Maltese.csv", row.names = FALSE)
write.csv(Nuer,"Nuer.csv", row.names = FALSE)
write.csv(Nepali,"Nepali.csv", row.names = FALSE)
write.csv(Armenian,"Armenian.csv", row.names = FALSE)
write.csv(SouthernAsianNfd,"SouthernAsianNfd.csv", row.names = FALSE)
write.csv(Lao,"Lao.csv", row.names = FALSE)
write.csv(Portugese,"Portugese.csv", row.names = FALSE)
write.csv(Marathi,"Marathi.csv", row.names = FALSE)
write.csv(Japanese,"Japanese.csv", row.names = FALSE)
```

## READ IN THE DATA

Dan <- read.csv("t3_final_Dan_.csv", stringsAsFactors = TRUE, header = FALSE)

# Batch 4

```{r}
DanSerboCroatYugo <- read.csv("t3_final_Dan_Serbo_Croat_Yugo_sodescribed.csv", stringsAsFactors = TRUE, header = FALSE)
DanDutch <- read.csv("t3_final_Dan_Dutch.csv", stringsAsFactors = TRUE, header = FALSE)
DanSwahili <- read.csv("t3_final_Dan_Swahili.csv", stringsAsFactors = TRUE, header = FALSE)
DanFrenchCreoleNfd <- read.csv("t3_final_Dan_French_Creole_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanKaren <- read.csv("t3_final_Dan_Karen.csv", stringsAsFactors = TRUE, header = FALSE)
DanCreoleNfd <- read.csv("t3_final_Dan_Creole_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanAmharic <- read.csv("t3_final_Dan_Amharic.csv", stringsAsFactors = TRUE, header = FALSE)
DanDinka <- read.csv("t3_final_Dan_Dinka.csv", stringsAsFactors = TRUE, header = FALSE)
DanShona <- read.csv("t3_final_Dan_Shona.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaori_NZ <- read.csv("t3_final_Dan_Maori_NZ.csv", stringsAsFactors = TRUE, header = FALSE)
DanUkrainian <- read.csv("t3_final_Dan_Ukrainian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHarari <- read.csv("t3_final_Dan_Harari.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfrikaans <- read.csv("t3_final_Dan_Afrikaans.csv", stringsAsFactors = TRUE, header = FALSE)
DanTongan <- read.csv("t3_final_Dan_Tongan.csv", stringsAsFactors = TRUE, header = FALSE)
DanCzech <- read.csv("t3_final_Dan_Czech.csv", stringsAsFactors = TRUE, header = FALSE)
DanKonkani <- read.csv("t3_final_Dan_Konkani.csv", stringsAsFactors = TRUE, header = FALSE)
DanKrio <- read.csv("t3_final_Dan_Krio.csv", stringsAsFactors = TRUE, header = FALSE)
DanTibetan <- read.csv("t3_final_Dan_Tibetan.csv", stringsAsFactors = TRUE, header = FALSE)
DanUygur <- read.csv("t3_final_Dan_Uygur.csv", stringsAsFactors = TRUE, header = FALSE)
DanIranic <- read.csv("t3_final_Dan_Iranic.csv", stringsAsFactors = TRUE, header = FALSE)
```

## APPLY FUNCTIONS

**tidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
# save output with Dan prefix removed
SerboCroatYugo <- tidy(DanSerboCroatYugo)
Dutch <- tidy(DanDutch)
Swahili <- tidy(DanSwahili)
FrenchCreoleNfd <- tidy(DanFrenchCreoleNfd)
Karen <- tidy(DanKaren)
CreoleNfd <- tidy(DanCreoleNfd)
Amharic <- tidy(DanAmharic)
Dinka <- tidy(DanDinka)
Shona <- tidy(DanShona)
MaoriNZ <- tidy(DanMaori_NZ)
Ukrainian <- tidy(DanUkrainian)
Harari <- tidy(DanHarari)
Afrikaans <- tidy(DanAfrikaans)
Tongan <- tidy(DanTongan)
Czech <- tidy(DanCzech)
Konkani <- tidy(DanKonkani)
Krio <- tidy(DanKrio)
Tibetan <- tidy(DanTibetan)
Uygur <- tidy(DanUygur)
Iranic <- tidy(DanIranic)
```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(SerboCroatYugo,"SerboCroatYugo.csv", row.names = FALSE)
write.csv(Dutch,"Dutch.csv", row.names = FALSE)
write.csv(Swahili,"Swahili.csv", row.names = FALSE)
write.csv(FrenchCreoleNfd,"FrenchCreoleNfd.csv", row.names = FALSE)
write.csv(Karen,"Karen.csv", row.names = FALSE)
write.csv(CreoleNfd,"CreoleNfd.csv", row.names = FALSE)
write.csv(Amharic,"Amharic.csv", row.names = FALSE)
write.csv(Dinka,"Dinka.csv", row.names = FALSE)
write.csv(Shona,"Shona.csv", row.names = FALSE)
write.csv(MaoriNZ,"MaoriNZ.csv", row.names = FALSE)
write.csv(Ukrainian,"Ukrainian.csv", row.names = FALSE)
write.csv(Harari,"Harari.csv", row.names = FALSE)
write.csv(Afrikaans,"Afrikaans.csv", row.names = FALSE)
write.csv(Tongan,"Tongan.csv", row.names = FALSE)
write.csv(Czech,"Czech.csv", row.names = FALSE)
write.csv(Konkani,"Konkani.csv", row.names = FALSE)
write.csv(Krio,"Krio.csv", row.names = FALSE)
write.csv(Tibetan,"Tibetan.csv", row.names = FALSE)
write.csv(Uygur,"Uygur.csv", row.names = FALSE)
write.csv(Iranic,"Iranic.csv", row.names = FALSE)
```

## READ IN THE DATA

Dan <- read.csv("t3_final_Dan_.csv", stringsAsFactors = TRUE, header = FALSE)

# Batch 5

```{r}
DanShilluk <- read.csv("t3_final_Dan_Shilluk.csv", stringsAsFactors = TRUE, header = FALSE)
DanKirundi <- read.csv("t3_final_Dan_Kirundi.csv", stringsAsFactors = TRUE, header = FALSE)
DanFijian <- read.csv("t3_final_Dan_Fijian.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfricanLangNec <- read.csv("t3_final_Dan_African_Lang_nec.csv", stringsAsFactors = TRUE, header = FALSE)
DanSlovene <- read.csv("t3_final_Dan_Slovene.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfricanLangNfd <- read.csv("t3_final_Dan_African_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanChaldeanNeoAramaic <- read.csv("t3_final_Dan_Chaldean_Neo_Aramaic.csv", stringsAsFactors = TRUE, header = FALSE)
DanKurdish <- read.csv("t3_final_Dan_Kurdish.csv", stringsAsFactors = TRUE, header = FALSE)
DanMon <- read.csv("t3_final_Dan_Mon.csv", stringsAsFactors = TRUE, header = FALSE)
DanSlovak <- read.csv("t3_final_Dan_Slovak.csv", stringsAsFactors = TRUE, header = FALSE)
DanBisaya <- read.csv("t3_final_Dan_Bisaya.csv", stringsAsFactors = TRUE, header = FALSE)
DanIndoAryanNfd <- read.csv("t3_final_Dan_Indo_Aryan_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanTetum <- read.csv("t3_final_Dan_Tetum.csv", stringsAsFactors = TRUE, header = FALSE)
DanTulu <- read.csv("t3_final_Dan_Tulu.csv", stringsAsFactors = TRUE, header = FALSE)
DanFijianHindustani <- read.csv("t3_final_Dan_Fijian_Hindustani.csv", stringsAsFactors = TRUE, header = FALSE)
DanTimorese <- read.csv("t3_final_Dan_Timorese.csv", stringsAsFactors = TRUE, header = FALSE)
DanYoruba <- read.csv("t3_final_Dan_Yoruba.csv", stringsAsFactors = TRUE, header = FALSE)
DanFinnish <- read.csv("t3_final_Dan_Finnish.csv", stringsAsFactors = TRUE, header = FALSE)
DanBulgarian <- read.csv("t3_final_Dan_Bulgarian.csv", stringsAsFactors = TRUE, header = FALSE)
DanCebuano <- read.csv("t3_final_Dan_Cebuano.csv", stringsAsFactors = TRUE, header = FALSE)
```

## APPLY FUNCTIONS

**tidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
Shilluk <- tidy(DanShilluk)
Kirundi <- tidy(DanKirundi)
Fijian <- tidy(DanFijian)
AfricanLangNec <- tidy(DanAfricanLangNec)
Slovene <- tidy(DanSlovene)
AfricanLangNfd <- tidy(DanAfricanLangNfd)
ChaldeanNeoAramaic <- tidy(DanChaldeanNeoAramaic)
Kurdish <- tidy(DanKurdish)
Mon <- tidy(DanMon)
Slovak <- tidy(DanSlovak)
Bisaya <- tidy(DanBisaya)
IndoAryanNfd <- tidy(DanIndoAryanNfd)
Tetum <- tidy(DanTetum)
Tulu <- tidy(DanTulu)
FijianHindustani <- tidy(DanFijianHindustani)
Timorese <- tidy(DanTimorese)
Yoruba <- tidy(DanYoruba)
Finnish <- tidy(DanFinnish)
Bulgarian <- tidy(DanBulgarian)
Cebuano <-tidy(DanCebuano)
```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(Shilluk,"Shilluk.csv", row.names = FALSE)
write.csv(Kirundi,"Kirundi.csv", row.names = FALSE)
write.csv(Fijian,"Fijian.csv", row.names = FALSE)
write.csv(AfricanLangNec,"AfricanLangNec.csv", row.names = FALSE)
write.csv(Slovene,"Slovene.csv", row.names = FALSE)
write.csv(AfricanLangNfd,"AfricanLangNfd.csv", row.names = FALSE)
write.csv(ChaldeanNeoAramaic,"ChaldeanNeoAramaic.csv", row.names = FALSE)
write.csv(Kurdish,"Kurdish.csv", row.names = FALSE)
write.csv(Mon,"Mon.csv", row.names = FALSE)
write.csv(Slovak,"Slovak.csv", row.names = FALSE)
write.csv(Bisaya,"Bisaya.csv", row.names = FALSE)
write.csv(IndoAryanNfd,"IndoAryanNfd.csv", row.names = FALSE)
write.csv(Tetum,"Tetum.csv", row.names = FALSE)
write.csv(Tulu,"Tulu.csv", row.names = FALSE)
write.csv(FijianHindustani,"FijianHindustani.csv", row.names = FALSE)
write.csv(Timorese,"Timorese.csv", row.names = FALSE)
write.csv(Yoruba,"Yoruba.csv", row.names = FALSE)
write.csv(Finnish,"Finnish.csv", row.names = FALSE)
write.csv(Bulgarian,"Bulgarian.csv", row.names = FALSE)
write.csv(Cebuano,"Cebuano.csv", row.names = FALSE)
```

## READ IN THE DATA

Dan <- read.csv("t3_final_Dan_.csv", stringsAsFactors = TRUE, header = FALSE)

# Batch 6

```{r}
DanHebrew <- read.csv("t3_final_Dan_Hebrew.csv", stringsAsFactors = TRUE, header = FALSE)
DanKinyarwanda <- read.csv("t3_final_Dan_Kinyarwanda.csv", stringsAsFactors = TRUE, header = FALSE)
DanIgbo <- read.csv("t3_final_Dan_Igbo.csv", stringsAsFactors = TRUE, header = FALSE)
DanNdebele <- read.csv("t3_final_Dan_Ndebele.csv", stringsAsFactors = TRUE, header = FALSE)
DanPidginNfd <- read.csv("t3_final_Dan_Pidgin_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanHausa <- read.csv("t3_final_Dan_Hausa.csv", stringsAsFactors = TRUE, header = FALSE)
DanOriya <- read.csv("t3_final_Dan_Oriya.csv", stringsAsFactors = TRUE, header = FALSE)
DanTokPisin <- read.csv("t3_final_Dan_Tok_Pisin.csv", stringsAsFactors = TRUE, header = FALSE)
DanChinHaka <- read.csv("t3_final_Dan_Chin_Haka.csv", stringsAsFactors = TRUE, header = FALSE)
DanAcholi <- read.csv("t3_final_Dan_Acholi.csv", stringsAsFactors = TRUE, header = FALSE)
DanTigre <- read.csv("t3_final_Dan_Tigre.csv", stringsAsFactors = TRUE, header = FALSE)
DanAkan <- read.csv("t3_final_Dan_Akan.csv", stringsAsFactors = TRUE, header = FALSE)
DanIlokano <- read.csv("t3_final_Dan_Ilokano.csv", stringsAsFactors = TRUE, header = FALSE)
```

## APPLY FUNCTIONS

**tidy & save output with Dan prefix removed**
y <- tidy(x)

```{r}
Hebrew <- tidy(DanHebrew)
Kinyarwanda <- tidy(DanKinyarwanda)
Igbo <- tidy(DanIgbo)
Ndebele <- tidy(DanNdebele)
PidginNfd <- tidy(DanPidginNfd)
Hausa <- tidy(DanHausa)
Oriya <- tidy(DanOriya)
TokPisin <- tidy(DanTokPisin)
ChinHaka <- tidy(DanChinHaka)
Acholi <- tidy(DanAcholi)
Tigre <- tidy(DanTigrinya)
Akan <- tidy(DanAkan)
Ilokano <-tidy(DanIlokano)
```

## EXPORT OUTPUT

write.csv(y,"y.csv", row.names = FALSE)

```{r}
write.csv(Hebrew,"Hebrew.csv", row.names = FALSE)
write.csv(Kinyarwanda,"Kinyarwanda.csv", row.names = FALSE)
write.csv(Igbo,"Igbo.csv", row.names = FALSE)
write.csv(Ndebele,"Ndebele.csv", row.names = FALSE)
write.csv(PidginNfd,"PidginNfd.csv", row.names = FALSE)
write.csv(Hausa,"Hausa.csv", row.names = FALSE)
write.csv(Oriya,"Oriya.csv", row.names = FALSE)
write.csv(TokPisin,"TokPisin.csv", row.names = FALSE)
write.csv(ChinHaka,"ChinHaka.csv", row.names = FALSE)
write.csv(Acholi,"Acholi.csv", row.names = FALSE)
write.csv(Tigre,"Tigre.csv", row.names = FALSE)
write.csv(Akan,"Akan.csv", row.names = FALSE)
write.csv(Ilokano,"Ilokano.csv", row.names = FALSE)
```

