---
title: "1_import_tidy"
author: "Fiona Neilson"
date: "23/06/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1 DATA PRE-PROCESSING

## 1.1 Import libraries


```{r, message=FALSE, warning=FALSE}
library(tidyr) 
library(dplyr) 
library(tibble)
library(forcats)
library(stringr)
library(tidyverse)
```

## 1.2 Read in the data

I manually read in 112 CSV files with ABS microdata. The Dan prefix refers to 'City of Greater Dandenong', which is the Local Government Area or council name. Note: As I was not experienced in writing functions at the time of this work, I created a line of code per file. 

```{r}
# 1 
DanSerbian <- read.csv("t3_final_Dan_Serbian.csv", stringsAsFactors = TRUE, header = FALSE)
DanSinhalese <- read.csv("t3_final_Dan_Sinhalese.csv", stringsAsFactors = TRUE, header = FALSE)
DanSpanish <- read.csv("t3_final_Dan_Spanish.csv", stringsAsFactors = TRUE, header = FALSE)
DanTamil <- read.csv("t3_final_Dan_Tamil.csv", stringsAsFactors = TRUE, header = FALSE)
DanTurkish <- read.csv("t3_final_Dan_Turkish.csv", stringsAsFactors = TRUE, header = FALSE)
DanUrdu <- read.csv("t3_final_Dan_Urdu.csv", stringsAsFactors = TRUE, header = FALSE)
DanAlbanian <- read.csv("t3_final_Dan_Albanian.csv", stringsAsFactors = TRUE, header = FALSE)
DanBurmese <- read.csv("t3_final_Dan_Burmese.csv", stringsAsFactors = TRUE, header = FALSE)
DanHindi <- read.csv("t3_final_Dan_Hindi.csv", stringsAsFactors = TRUE, header = FALSE)
DanItalian <- read.csv("t3_final_Dan_Italian.csv", stringsAsFactors = TRUE, header = FALSE)
DanArabic <- read.csv("t3_final_Dan_Arabic.csv", stringsAsFactors = TRUE, header = FALSE)
DanCantonese <- read.csv("t3_final_Dan_Cantonese.csv", stringsAsFactors = TRUE, header = FALSE)
DanDari <- read.csv("t3_final_Dan_Dari.csv", stringsAsFactors = TRUE, header = FALSE)
DanGreek <- read.csv("t3_final_Dan_Greek.csv", stringsAsFactors = TRUE, header = FALSE)
DanHazaraghi <- read.csv("t3_final_Dan_Hazaraghi.csv", stringsAsFactors = TRUE, header = FALSE)
DanKhmer <- read.csv("t3_final_Dan_Khmer.csv", stringsAsFactors = TRUE, header = FALSE)
DanMandarin <- read.csv("t3_final_Dan_Mandarin.csv", stringsAsFactors = TRUE, header = FALSE)
DanPunjabi <- read.csv("t3_final_Dan_Punjabi.csv", stringsAsFactors = TRUE, header = FALSE)
DanTigrinya <- read.csv("t3_final_Dan_Tigrinya.csv", stringsAsFactors = TRUE, header = FALSE)
DanVietnamese <- read.csv("t3_final_Dan_Vietnamese.csv", stringsAsFactors = TRUE, header = FALSE)
# 2
DanBosnian <- read.csv("t3_final_Dan_Bosnian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMalayalam <- read.csv("t3_final_Dan_Malayalam.csv", stringsAsFactors = TRUE, header = FALSE)
DanTagalog <- read.csv("t3_final_Dan_Tagalog.csv", stringsAsFactors = TRUE, header = FALSE)
DanFrench <- read.csv("t3_final_Dan_French.csv", stringsAsFactors = TRUE, header = FALSE)
DanPersian_ex_Dari <- read.csv("t3_final_Dan_Persian_ex_Dari.csv", stringsAsFactors = TRUE, header = FALSE)
DanCroatian <- read.csv("t3_final_Dan_Croatian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMin_Nan <- read.csv("t3_final_Dan_Min_Nan.csv", stringsAsFactors = TRUE, header = FALSE)
DanPashto <- read.csv("t3_final_Dan_Pashto.csv", stringsAsFactors = TRUE, header = FALSE)
DanPolish <- read.csv("t3_final_Dan_Polish.csv", stringsAsFactors = TRUE, header = FALSE)
DanSamoan <- read.csv("t3_final_Dan_Samoan.csv", stringsAsFactors = TRUE, header = FALSE)
DanFilipino <- read.csv("t3_final_Dan_Filipino.csv", stringsAsFactors = TRUE, header = FALSE)
DanBengali <- read.csv("t3_final_Dan_Bengali.csv", stringsAsFactors = TRUE, header = FALSE)
DanTelugu <- read.csv("t3_final_Dan_Telugu.csv", stringsAsFactors = TRUE, header = FALSE)
DanGujarati <- read.csv("t3_final_Dan_Gujarati.csv", stringsAsFactors = TRUE, header = FALSE)
DanIndonesian <- read.csv("t3_final_Dan_Indonesian.csv", stringsAsFactors = TRUE, header = FALSE)
DanRohingya <- read.csv("t3_final_Dan_Rohingya.csv", stringsAsFactors = TRUE, header = FALSE)
DanThai <- read.csv("t3_final_Dan_Thai.csv", stringsAsFactors = TRUE, header = FALSE)
DanRussian <- read.csv("t3_final_Dan_Russian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHungarian <- read.csv("t3_final_Dan_Hungarian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHakka <- read.csv("t3_final_Dan_Hakka.csv", stringsAsFactors = TRUE, header = FALSE)
# 3
DanKorean <- read.csv("t3_final_Dan_Korean.csv", stringsAsFactors = TRUE, header = FALSE)
DanRomanian <- read.csv("t3_final_Dan_Romanian.csv", stringsAsFactors = TRUE, header = FALSE)
DanKannada <- read.csv("t3_final_Dan_Kannada.csv", stringsAsFactors = TRUE, header = FALSE)
DanMacedonian <- read.csv("t3_final_Dan_Macedonian.csv", stringsAsFactors = TRUE, header = FALSE)
DanMalay <- read.csv("t3_final_Dan_Malay.csv", stringsAsFactors = TRUE, header = FALSE)
DanSomali <- read.csv("t3_final_Dan_Somali.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaoriCookIsland <- read.csv("t3_final_Dan_Maori_Cook_Island.csv", stringsAsFactors = TRUE, header = FALSE)
DanGerman <- read.csv("t3_final_Dan_German.csv", stringsAsFactors = TRUE, header = FALSE)
DanChineseNfd <- read.csv("t3_final_Dan_Chinese_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanMauritianCreole <- read.csv("t3_final_Dan_Mauritian_Creole.csv", stringsAsFactors = TRUE, header = FALSE)
DanOromo <- read.csv("t3_final_Dan_Oromo.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaltese <- read.csv("t3_final_Dan_Maltese.csv", stringsAsFactors = TRUE, header = FALSE)
DanNuer <- read.csv("t3_final_Dan_Nuer.csv", stringsAsFactors = TRUE, header = FALSE)
DanNepali <- read.csv("t3_final_Dan_Nepali.csv", stringsAsFactors = TRUE, header = FALSE)
DanArmenian <- read.csv("t3_final_Dan_Armenian.csv", stringsAsFactors = TRUE, header = FALSE)
DanSouthernAsianNfd <- read.csv("t3_final_Dan_Southern_Asian_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanLao <- read.csv("t3_final_Dan_Lao.csv", stringsAsFactors = TRUE, header = FALSE)
DanPortugese <- read.csv("t3_final_Dan_Portugese.csv", stringsAsFactors = TRUE, header = FALSE)
DanMarathi <- read.csv("t3_final_Dan_Marathi.csv", stringsAsFactors = TRUE, header = FALSE)
DanJapanese <- read.csv("t3_final_Dan_Japanese.csv", stringsAsFactors = TRUE, header = FALSE)
# 4
DanSerboCroatYugo <- read.csv("t3_final_Dan_Serbo_Croat_Yugo_sodescribed.csv", stringsAsFactors = TRUE, header = FALSE)
DanDutch <- read.csv("t3_final_Dan_Dutch.csv", stringsAsFactors = TRUE, header = FALSE)
DanSwahili <- read.csv("t3_final_Dan_Swahili.csv", stringsAsFactors = TRUE, header = FALSE)
DanFrenchCreoleNfd <- read.csv("t3_final_Dan_French_Creole_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanKaren <- read.csv("t3_final_Dan_Karen.csv", stringsAsFactors = TRUE, header = FALSE)
DanCreoleNfd <- read.csv("t3_final_Dan_Creole_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanAmharic <- read.csv("t3_final_Dan_Amharic.csv", stringsAsFactors = TRUE, header = FALSE)
DanDinka <- read.csv("t3_final_Dan_Dinka.csv", stringsAsFactors = TRUE, header = FALSE)
DanShona <- read.csv("t3_final_Dan_Shona.csv", stringsAsFactors = TRUE, header = FALSE)
DanMaori_NZ <- read.csv("t3_final_Dan_Maori_NZ.csv", stringsAsFactors = TRUE, header = FALSE)
DanUkrainian <- read.csv("t3_final_Dan_Ukrainian.csv", stringsAsFactors = TRUE, header = FALSE)
DanHarari <- read.csv("t3_final_Dan_Harari.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfrikaans <- read.csv("t3_final_Dan_Afrikaans.csv", stringsAsFactors = TRUE, header = FALSE)
DanTongan <- read.csv("t3_final_Dan_Tongan.csv", stringsAsFactors = TRUE, header = FALSE)
DanCzech <- read.csv("t3_final_Dan_Czech.csv", stringsAsFactors = TRUE, header = FALSE)
DanKonkani <- read.csv("t3_final_Dan_Konkani.csv", stringsAsFactors = TRUE, header = FALSE)
DanKrio <- read.csv("t3_final_Dan_Krio.csv", stringsAsFactors = TRUE, header = FALSE)
DanTibetan <- read.csv("t3_final_Dan_Tibetan.csv", stringsAsFactors = TRUE, header = FALSE)
DanUygur <- read.csv("t3_final_Dan_Uygur.csv", stringsAsFactors = TRUE, header = FALSE)
DanIranic <- read.csv("t3_final_Dan_Iranic.csv", stringsAsFactors = TRUE, header = FALSE)
# 5
DanShilluk <- read.csv("t3_final_Dan_Shilluk.csv", stringsAsFactors = TRUE, header = FALSE)
DanKirundi <- read.csv("t3_final_Dan_Kirundi.csv", stringsAsFactors = TRUE, header = FALSE)
DanFijian <- read.csv("t3_final_Dan_Fijian.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfricanLangNec <- read.csv("t3_final_Dan_African_Lang_nec.csv", stringsAsFactors = TRUE, header = FALSE)
DanSlovene <- read.csv("t3_final_Dan_Slovene.csv", stringsAsFactors = TRUE, header = FALSE)
DanAfricanLangNfd <- read.csv("t3_final_Dan_African_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanChaldeanNeoAramaic <- read.csv("t3_final_Dan_Chaldean_Neo_Aramaic.csv", stringsAsFactors = TRUE, header = FALSE)
DanKurdish <- read.csv("t3_final_Dan_Kurdish.csv", stringsAsFactors = TRUE, header = FALSE)
DanMon <- read.csv("t3_final_Dan_Mon.csv", stringsAsFactors = TRUE, header = FALSE)
DanSlovak <- read.csv("t3_final_Dan_Slovak.csv", stringsAsFactors = TRUE, header = FALSE)
DanBisaya <- read.csv("t3_final_Dan_Bisaya.csv", stringsAsFactors = TRUE, header = FALSE)
DanIndoAryanNfd <- read.csv("t3_final_Dan_Indo_Aryan_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanTetum <- read.csv("t3_final_Dan_Tetum.csv", stringsAsFactors = TRUE, header = FALSE)
DanTulu <- read.csv("t3_final_Dan_Tulu.csv", stringsAsFactors = TRUE, header = FALSE)
DanFijianHindustani <- read.csv("t3_final_Dan_Fijian_Hindustani.csv", stringsAsFactors = TRUE, header = FALSE)
DanTimorese <- read.csv("t3_final_Dan_Timorese.csv", stringsAsFactors = TRUE, header = FALSE)
DanYoruba <- read.csv("t3_final_Dan_Yoruba.csv", stringsAsFactors = TRUE, header = FALSE)
DanFinnish <- read.csv("t3_final_Dan_Finnish.csv", stringsAsFactors = TRUE, header = FALSE)
DanBulgarian <- read.csv("t3_final_Dan_Bulgarian.csv", stringsAsFactors = TRUE, header = FALSE)
DanCebuano <- read.csv("t3_final_Dan_Cebuano.csv", stringsAsFactors = TRUE, header = FALSE)
# 6
DanHebrew <- read.csv("t3_final_Dan_Hebrew.csv", stringsAsFactors = TRUE, header = FALSE)
DanKinyarwanda <- read.csv("t3_final_Dan_Kinyarwanda.csv", stringsAsFactors = TRUE, header = FALSE)
DanIgbo <- read.csv("t3_final_Dan_Igbo.csv", stringsAsFactors = TRUE, header = FALSE)
DanNdebele <- read.csv("t3_final_Dan_Ndebele.csv", stringsAsFactors = TRUE, header = FALSE)
DanPidginNfd <- read.csv("t3_final_Dan_Pidgin_nfd.csv", stringsAsFactors = TRUE, header = FALSE)
DanHausa <- read.csv("t3_final_Dan_Hausa.csv", stringsAsFactors = TRUE, header = FALSE)
DanOriya <- read.csv("t3_final_Dan_Oriya.csv", stringsAsFactors = TRUE, header = FALSE)
DanTokPisin <- read.csv("t3_final_Dan_Tok_Pisin.csv", stringsAsFactors = TRUE, header = FALSE)
DanChinHaka <- read.csv("t3_final_Dan_Chin_Haka.csv", stringsAsFactors = TRUE, header = FALSE)
DanAcholi <- read.csv("t3_final_Dan_Acholi.csv", stringsAsFactors = TRUE, header = FALSE)
DanTigre <- read.csv("t3_final_Dan_Tigre.csv", stringsAsFactors = TRUE, header = FALSE)
DanAkan <- read.csv("t3_final_Dan_Akan.csv", stringsAsFactors = TRUE, header = FALSE)
DanIlokano <- read.csv("t3_final_Dan_Ilokano.csv", stringsAsFactors = TRUE, header = FALSE)
```

## 1.3 Transpose data, including variable names, and gather columns

### 1.3.1 Create function

I created a custom function to reformat the ABS data files into tidy data format, including transposing (turning rows into columns) and combining separate Male and Female columns into one.

```{r}
# define tidy function
tidy <- function(x) {
  x2 <- data.frame(t(x[-1]))
  colnames(x2) <- x[, 1]
  x2 <- remove_rownames(x2)
  x3 <- x2 %>% gather(Male, Female, key = "SEXP", value = "total")
}
```


### 1.3.2 Apply function

As mentioned above, I was not yet proficient in writing functions that would automate the upload and application of the tidying function, so I created one line of code for every data file. 

```{r}
# tidy and save output with Dan prefix removed
Serbian <- tidy(DanSerbian)
Sinhalese <- tidy(DanSinhalese)
Spanish <- tidy(DanSpanish)
Tamil <- tidy(DanTamil)
Turkish <- tidy(DanTurkish)
Urdu <- tidy(DanUrdu)
Albanian <- tidy(DanAlbanian)
Burmese <- tidy(DanBurmese)
Hindi <- tidy(DanHindi)
Italian <- tidy(DanItalian)
Arabic <- tidy(DanArabic)
Cantonese <- tidy(DanCantonese)
Dari<- tidy(DanDari)
Greek <- tidy(DanGreek)
Hazaraghi <- tidy(DanHazaraghi)
Khmer <- tidy(DanKhmer)
Mandarin <- tidy(DanMandarin)
Punjabi <- tidy(DanPunjabi)
Tigrinya <- tidy(DanTigrinya)
Vietnamese <- tidy(DanVietnamese)
# 
Bosnian <- tidy(DanBosnian)
Malayalam <- tidy(DanMalayalam)
Tagalog <- tidy(DanTagalog)
French <- tidy(DanFrench)
Persian_ex_Dari <- tidy(DanPersian_ex_Dari)
Croatian <- tidy(DanCroatian)
Min_Nan <- tidy(DanMin_Nan)
Pashto <- tidy(DanPashto)
Polish <- tidy(DanPolish)
Samoan <- tidy(DanSamoan)
Filipino <- tidy(DanFilipino)
Bengali <- tidy(DanBengali)
Telugu <- tidy(DanTelugu)
Gujarati <- tidy(DanGujarati)
Indonesian <- tidy(DanIndonesian)
Rohingya <- tidy(DanRohingya)
Thai <- tidy(DanThai)
Russian <- tidy(DanRussian)
Hungarian <- tidy(DanHungarian)
Hakka <- tidy(DanHakka)
# 
Korean <- tidy(DanKorean) 
Romanian <- tidy(DanRomanian)
Kannada  <- tidy(DanKannada) 
Macedonian <- tidy(DanMacedonian) 
Malay <- tidy(DanMalay)
Somali <- tidy(DanSomali)
MaoriCookIsland  <- tidy(DanMaoriCookIsland) 
German <- tidy(DanGerman) 
ChineseNfd  <- tidy(DanChineseNfd)
MauritianCreole  <- tidy(DanMauritianCreole) 
Oromo <- tidy(DanOromo)
Maltese  <- tidy(DanMaltese) 
Nuer  <- tidy(DanNuer)
Nepali  <- tidy(DanNepali)
Armenian <- tidy(DanArmenian)
SouthernAsianNfd <- tidy(DanSouthernAsianNfd) 
Lao <- tidy(DanLao) 
Portugese <- tidy(DanPortugese)
Marathi <- tidy(DanMarathi) 
Japanese <- tidy(DanJapanese) 
# 
SerboCroatYugo <- tidy(DanSerboCroatYugo)
Dutch <- tidy(DanDutch)
Swahili <- tidy(DanSwahili)
FrenchCreoleNfd <- tidy(DanFrenchCreoleNfd)
Karen <- tidy(DanKaren)
CreoleNfd <- tidy(DanCreoleNfd)
Amharic <- tidy(DanAmharic)
Dinka <- tidy(DanDinka)
Shona <- tidy(DanShona)
MaoriNZ <- tidy(DanMaori_NZ)
Ukrainian <- tidy(DanUkrainian)
Harari <- tidy(DanHarari)
Afrikaans <- tidy(DanAfrikaans)
Tongan <- tidy(DanTongan)
Czech <- tidy(DanCzech)
Konkani <- tidy(DanKonkani)
Krio <- tidy(DanKrio)
Tibetan <- tidy(DanTibetan)
Uygur <- tidy(DanUygur)
Iranic <- tidy(DanIranic)
Shilluk <- tidy(DanShilluk)
Kirundi <- tidy(DanKirundi)
Fijian <- tidy(DanFijian)
AfricanLangNec <- tidy(DanAfricanLangNec)
Slovene <- tidy(DanSlovene)
AfricanLangNfd <- tidy(DanAfricanLangNfd)
ChaldeanNeoAramaic <- tidy(DanChaldeanNeoAramaic)
Kurdish <- tidy(DanKurdish)
Mon <- tidy(DanMon)
Slovak <- tidy(DanSlovak)
Bisaya <- tidy(DanBisaya)
IndoAryanNfd <- tidy(DanIndoAryanNfd)
Tetum <- tidy(DanTetum)
Tulu <- tidy(DanTulu)
FijianHindustani <- tidy(DanFijianHindustani)
Timorese <- tidy(DanTimorese)
Yoruba <- tidy(DanYoruba)
Finnish <- tidy(DanFinnish)
Bulgarian <- tidy(DanBulgarian)
Cebuano <-tidy(DanCebuano)
Hebrew <- tidy(DanHebrew)
Kinyarwanda <- tidy(DanKinyarwanda)
Igbo <- tidy(DanIgbo)
Ndebele <- tidy(DanNdebele)
PidginNfd <- tidy(DanPidginNfd)
Hausa <- tidy(DanHausa)
Oriya <- tidy(DanOriya)
TokPisin <- tidy(DanTokPisin)
ChinHaka <- tidy(DanChinHaka)
Acholi <- tidy(DanAcholi)
Tigre <- tidy(DanTigrinya)
Akan <- tidy(DanAkan)
Ilokano <-tidy(DanIlokano)
```

## 1.4 Merge dataframes into master dataframe

I combined 112 separate files into one dataframe. 

```{r}
AllLangs <- rbind(Vietnamese, Greek, Sinhalese, Hazaraghi, Tamil, Dari, Arabic, Hindi, Italian, Khmer, Punjabi, Mandarin, Cantonese, Serbian, Albanian, Turkish, Burmese, Spanish, Urdu, Bosnian, Malayalam, Tagalog, French, Persian_ex_Dari, Croatian, Min_Nan, Pashto, Polish, Samoan, Filipino, Bengali, Telugu, Gujarati, Indonesian, Rohingya, Thai, Russian, Hungarian, Hakka, Korean,Romanian,Kannada,Macedonian,Malay,Somali,MaoriCookIsland,German,ChineseNfd,MauritianCreole,Oromo,Maltese,Nuer,Nepali,Armenian,SouthernAsianNfd,Lao,Portugese,Marathi,Japanese,AfricanLangNfd,ChaldeanNeoAramaic,Kurdish,Mon,Slovak,Bisaya,IndoAryanNfd,Tetum,Tulu,FijianHindustani,Timorese,Yoruba,Finnish,Bulgarian,Cebuano,Hebrew,Igbo,Ndebele,PidginNfd,Hausa,Oriya,TokPisin,ChinHaka,Acholi,Tigre,Akan,Ilokano,SerboCroatYugo,Dutch,Swahili,FrenchCreoleNfd,Karen,CreoleNfd,Amharic,Dinka,Shona,MaoriNZ,Ukrainian,Harari,Afrikaans,Tongan,Czech,Konkani,Krio,Tibetan,Uygur,Iranic,Shilluk,Kirundi,Fijian,AfricanLangNec,Slovene,Kinyarwanda)
```

### 1.4.1 Display dimensions

This shows that there are 5848 observations (rows) and 10 variables (columns).

```{r}
dim(AllLangs)
```

### 1.4.2 Display dataframe structure 

Here we see the 10 columns: 
* LGA - Local Government Area 
* LANP - Language Spoken at Home
* HEAP - Level of Highest Educational Attainment
* EETP - Engagement in Employment, Education and Training
* NEDD - Dwelling Internet Connection
* ENGP - Proficiency in Spoken English
* BPLP - Country of Birth of Person
* YARRP - Year of Arrival in Australia
* SEXP - Sex
* Count - Count of people

I have retained the ABS Census acronyms for consistency. As per my report, I combined some of the levels or sub-categories within each of these variables where I did not require the level of granularity provided. 

```{r}
str(AllLangs)
```

## 1.5 Remove zero values

I removed all rows with a value of 0 in the Count column. 

```{r}
# remove zero values
#3696
AllLangs <- AllLangs %>% filter(
  total > 0
)
```

This reduces the number of observations (rows) to 3696.

```{r}
# check reduced no. of rows
dim(AllLangs)
```

## 1.6 Clean column names

I removed spaces in column names as these kinds of 'invisible' spaces can impede analysis. 

```{r}
# tidy column names (remove spaces)
names(AllLangs) <- str_replace_all(names(AllLangs), c(" "=""))
colnames(AllLangs)
```

## 1.7 Assign variable class

I classified all variables. All except for total are categorical variables. 

```{r}
# set class for variables
AllLangs$LGA <- as.factor(AllLangs$LGA)
AllLangs$LANP <- as.factor(AllLangs$LANP)
AllLangs$HEAP <- as.factor(AllLangs$HEAP)
AllLangs$EETP <- as.factor(AllLangs$EETP)
AllLangs$NEDD <- as.factor(AllLangs$NEDD)
AllLangs$ENGP <- as.factor(AllLangs$ENGP)
AllLangs$BPLP <- as.factor(AllLangs$BPLP)
AllLangs$YARRP <- as.factor(AllLangs$YARRP)
AllLangs$SEXP <- as.factor(AllLangs$SEXP)
AllLangs$total <- as.numeric(AllLangs$total)
```


I then confirmed the class and looked at the levels within each categorical variable. 

```{r}
# check variable classification
str(AllLangs)
```

## 1.8 Order and clean factor levels

### 1.8.1 LGA - Local Government Area

```{r}
# review factor levels 
levels(AllLangs$LGA)
```

I tidied the name, removing white space and unnecessary text. 

```{r}
# recode
AllLangs <- AllLangs %>%
  mutate(LGA = fct_recode(LGA,
  "Greater_Dandenong" = "Greater Dandenong (C)"
  )) 
AllLangs %>% count(LGA)
```

### 1.8.2 HEAP - Level of Highest Educational Attainment

```{r}
# review factor levels - HEAP
levels(AllLangs$HEAP)
```

I ordered the educational levels from lowest to highest, so that subsequent analyses and visualisations follow this sequence:  Non Secondary > Secondary > Higher

```{r}
# reorder levels - HEAP
education <- c("Non_Secondary", "Secondary", "Higher") # create vector in correct order
education <- as.factor(education)
AllLangs$HEAP <- factor(AllLangs$HEAP, levels = education, ordered = TRUE)
levels(AllLangs$HEAP)
```

### 1.8.3 EETP - Engagement in Employment, Education and Training

```{r}
# review factor levels
levels(AllLangs$EETP)
```

I ordered the employment/ education/ training variable from lowest to highest level of engagement: 
Not Engaged > Partial > Fully

```{r}
# reorder levels 
engagement <- c("Not_Engaged", "Partial", "Fully") # create vector in correct order
engagement <- as.factor(engagement)
AllLangs$EETP <- factor(AllLangs$EETP, levels = engagement, ordered = TRUE)
levels(AllLangs$EETP)
```

### 1.8.4 NEDD - Dwelling Internet Connection

```{r}
# review factor levels
levels(AllLangs$NEDD)
```

I shortened these for display purposes and to help create more concise code.  

```{r}
#simplify levels
levels(AllLangs$NEDD) <- c("Internet","No_Internet")
levels(AllLangs$NEDD)
```

### 1.8.5 ENGP - Proficiency in Spoken English

```{r}
# review factor levels
levels(AllLangs$ENGP)
```

No changes required

### 1.8.6 YARRP - Year of Arrival in Australia

```{r}
# review factor levels
levels(AllLangs$YARRP)
```

I ordered these chronologically: Pre 2006 > 2006-15 > 2016

```{r}
# order levels: YARRP 
years <- c("Pre_2006", "2006-15", "2016") # create vector in correct order
years <- as.factor(years)
AllLangs$YARRP <- factor(AllLangs$YARRP, levels = years, ordered = TRUE)
levels(AllLangs$YARRP)
```

### 1.8.7 SEXP - Sex

```{r}
# review factor levels
levels(AllLangs$SEXP)
```

No changes required

### 1.8.8 LANP - Language Spoken at Home

```{r}
# review factor levels
levels(AllLangs$LANP)
```

## 1.9 Copy dataframe and rename

I made a copy of the dataframe and assigned a new name. This way I retained a copy of the dataframe before the join operation in 1.10, in case I needed to revert to it. 

```{r}
# copy dataframe & rename 
df<- AllLangs 
```

## 1.10 Join classifications

### 1.10.1 Upload languages classification

This is the ABS languages classification, Table 1.3 showing broad groups, narrow groups and individual languages. I cleaned and tidied this file prior to upload. 

```{r}
# upload classifications
LangsClass<- read.csv("langs-classification.csv", stringsAsFactors = TRUE, header = TRUE)
```

### 1.10.2 Clean levels

A preliminary check showed that a number of the language names in my dataframe did not match the ones in the classification, due to slight formatting differences in the source data. I made minor changes to match the dataframe terms to the ones in the classification, so they would join correctly. 

```{r}
# first need to remove the "," in LANP levels
levels(df$LANP) <- gsub(", nfd"," nfd", levels(df$LANP))
levels(df$LANP) <- gsub(", nec"," nec", levels(df$LANP))
```

```{r}
# clean more levels. Specify replacement name first, then the name being replaced. 
levels(df$LANP) <- gsub("Serbo-Croatian/Yugoslavian, so described","Serbo-Croatian/Yugoslavian so described", levels(df$LANP))
levels(df$LANP) <- gsub("Southern Asian Languages nfd","Southern Asian Languages", levels(df$LANP))

```


### 1.10.3 Join classifications by key

I used the classification's 4-digit language code to join on the 4-digit language name in my dataframe and combine the two files.

```{r}
# join using inner_join 
df <- df %>% 
  left_join(LangsClass, c("LANP"= "Language4DC"))
head(df)
```

### 1.10.4 Check for missing values

```{r}
# check for missing values
df[!complete.cases(df),]
```


### 1.10.5 Order levels

I ordered the levels in my dataframe to reflect the order in the languages classification. 

```{r}
# create vector in correct order
LangGroup <- c("Northern European Languages","Southern European Languages","Eastern European Languages","Southwest and Central Asian Languages","Southern Asian Languages","Southeast Asian Languages", "Eastern Asian Languages", "Australian Indigenous Languages", "Other Languages") 
LangGroup <- as.factor(LangGroup)
df$GroupName1DC<- factor(df$GroupName1DC, levels = LangGroup, ordered = TRUE)
```

## 1.11 Export file 

I exported the dataframe at this point as RStudio Cloud requires me to reload the data at the start of each new file. This step is not required in RStudio Desktop. I needed to use RStudio Cloud in order to knit these documents, as this function is not supported on my laptop. 

```{r}
write.csv(df, file="out_df.csv")
```


