---
title: "2_summarise"
author: "Fiona Neilson"
date: "23/06/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 2 SUMMARISE DATA

## 2.1 Import libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr) 
library(tibble)
library(stringr)
```

## 2.2 Read in dataframe

```{r}
df = read.csv("out_df.csv", header=TRUE)
```


## 2.3 Compute weighted counts

### 2.3.1 Sum of cases

```{r}
sum(df$total)
```

### 2.3.2 Counts per variable

#### 2.3.2.1 LANP - Language Spoken at Home

This shows the counts of people who speak languages other than English at home, in descending order. 

```{r}
df %>% count(LANP, wt = total) %>% arrange(desc(n))
```

#### 2.3.2.2 HEAP - Level of Highest Educational Attainment

```{r}
df %>% count(HEAP, wt = total) %>% arrange(match(HEAP, c("Higher", "Secondary", "Non-Secondary")))

```

#### 2.3.2.3 EETP - Engagement in Employment, Education and Training

```{r}
df %>% count(EETP, wt = total) %>% arrange(match(EETP, c("Fully", "Partial", "Not_Engaged")))
```

#### 2.3.2.4 NEDD - Dwelling Internet Connection

```{r}
df %>% count(NEDD, wt = total) 
```

#### 2.3.2.5 ENGP - Proficiency in Spoken English

```{r}
df %>% count(ENGP, wt = total)
```

#### 2.3.2.6 BPLP - Country of Birth 

```{r}
df %>% count(BPLP, wt = total) %>% arrange(desc(n)) %>% head(10)
```

#### 2.3.2.7 YARRP - Year of Arrival in Australia

```{r}
df %>% count(YARRP, wt = total) %>% arrange(desc(n))
```

#### 2.3.2.8 SEXP - Sex

```{r}
df %>% count(SEXP, wt = total)
```


## 2.4 Exploration

### 2.4.1 Combine variables and summarise

#### 2.4.2.1 For example, group Engagement in Employment, Education and Training with Internet Access. Show counts.

```{r}
df %>% select(EETP, NEDD, total) %>% head(10)
```

#### 2.4.2.2 Another example: group by Language Spoken at Home and Engagement in Employment, Education and Training. Show counts. 

```{r}
# grouping and summarising - arranged by population
df %>% group_by(LANP, EETP) %>% summarise(total_pop = sum(total)) %>% arrange(desc(total_pop))
```

#### 2.4.2.3 Another example: filter by language group and explore English proficiency. Show as percentage. 

```{r, message=FALSE, warning=FALSE}
# English proficiency by gender for a language group (Urdu)
df %>% filter(LANP == "Urdu") %>% group_by(ENGP, SEXP) %>% summarise(Total = sum(total)) %>% mutate(Grand_Total = sum(Total)) %>% mutate(Perc = Total / Grand_Total * 100)
```

#### 2.4.2.4 Another example: explore the relationship between Proficiency in Spoken English and those not engaged in Engagement in Employment, Education or Training. Show counts. 

```{r, message=FALSE, warning=FALSE}
# what relationship does English (ENGP) have with the portion of the Non_Engaged (EETP)? 
# 1 - select these groups
EETP_group <- df %>% 
  group_by(
    EETP, ENGP
      )
# 2 - summarise all levels
EETP_group %>% 
  summarise(total = sum(total))

# 3 filter to one level
NotEngaged <- EETP_group %>% 
  filter(
    EETP == "Not_Engaged"
  ) %>% 
  summarise(total = sum(total))
NotEngaged
```

#### 2.4.2.5 Another example: explore the relationship between Proficiency in Spoken English and Language Spoken at Home

```{r}
# what relationship does English Proficiency have with language spoken at home (LANP)? 
# 1 - select these groups
English <- df %>% 
  group_by(
    LANP, ENGP
      ) %>% 
  summarise(
    total = sum(total)
    )
English 
```
## 2.5 Export file 

```{r}
write.csv(df, file="out_2_df.csv")
```
